---
title: "Linear Models"
author: "Clement Mugenzi"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(p8105.datasets)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```


# Linear Regression


```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit the first linear model

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```





```{r}
fit

summary(fit)
coef(fit)
summary(fit)$coef
```

tidythe results instead

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
# another way to tidy is to use glance.
fit %>% 
  broom::glance()
```


## Tak a look at factor...

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```


refit the last model 

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()
```

## diagnostics (all about the residuals)

boro against residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() + ylim(-500, 500)
```


stars against residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() + ylim(-500, 500)
```


add some predictions 

```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

# Nesting data

Here, every increase in stars and how it affects price per boro.

```{r}
fit_interaction = 
  lm(price ~ stars * boro, data = nyc_airbnb) %>% 
  broom::tidy()

fit_interaction
```




```{r}
fit_interaction_1 = 
  nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
fit_interaction_1
```


Let's try to map this instead

```{r}
nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(boro, results) %>% 
  unnest(results)
```


```{r}
manhattan_nest_lm_res = 
  nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(neighborhood, results) %>% 
  unnest(results)
```

Here we are plotting neighbrohoods in manhattan and what it would cost if we moved from a private room to a shared room. it will cost less.

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


# Cross Validation 

All about model selection. Picking variables to go in your model. know confounders, covariates. What belongs in the model and what does not. `AIC:` comparison between two nonnested models. how well does the model fit, and how complex the model is. and whichever of those is better wins. a less complex model. Checkout `BIC` too!

Questions to ask ourselves:

1. Overfitting or underfitting?

2. which model works better for future dataset.

3. Do i have high bias? high variance?

4. how complex is the model?

5. which model makes the best predictions for future datasets?


**Prediction accuracy:**

splitting your dataset and build the model using one dataset then testing the model using the second dataset. Basically, splititing the dataset into `train` and `test` datasets.

there is also **automated variable selection** using **Lasso** or **regression trees**.


```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw() 
```



## Training and Testing

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```


## fit three models of varying goodness

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


lets' look at some fits

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```


```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```



```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```



Make predictions


```{r}
# Root mean squared error

rmse(linear_mod, train_df)
rmse(smooth_mod, train_df)
rmse(wiggly_mod, train_df)
```


Here, the `wiggly_mod` is doing better but it does not matter.


```{r}
# Root mean squared error

rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Therefore, the lesser the `RMSE` the better the model since errors are minimized. Always choose the model that test better on the `Test` dataset. Thus, here the `smooth_mod` is doing better.

## Cross Validation using `Modelr`

`cross_mc` splits the dataframe for us!!

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
cv_df
```

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```


try fitting the linear model with all these... and comparing them by `rmse`

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```


let us visualize this 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


**Smooth model wins!!**


# Bootstrapping 

simulated dataset

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

here the second plot has a high variability as x-axis increases which means the estimate of the slope is right but we cannot be confident of the confidence interval.

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```



```{r}
lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


```{r}
lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


## How can i bootstrap

write a function to draw a bootstrap sample based on the dataframe.

Here, subjects are not put back in the original population.

```{r}
sim_df_nonconst %>% 
  sample_frac(size = 1) %>% 
  arrange(x)
```

here we sampling but subjects are put back in the population. yield different results.

```{r}
sim_df_nonconst %>% 
  sample_frac(size = 1, replace = T) %>% 
  arrange(x)
```



```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```


Since there is replacement, the plots are different everytime we run the code.

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```


organize a dataframe... basically keeping track of the results we care about.

```{r}
boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```

do some kind of analysis. Again, here it is with replacement, so that is why we are getting different results everytime the code is ran.

```{r}
bootstraps_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)
```


summarize these results. calculating the standard deviation of the estimates. equivalent to the error term in the simple linear regression. basing inference on default procedures.... **read about bootstrapping on your own time**

```{r}
bootstraps_results %>% 
  group_by(term) %>% 
  summarise(se = sd(estimate))
```


## try the `modelr` package

```{r}
sim_df_nonconst %>% 
  bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```
## what if your assumptions are not wrong?
with a different data input.

```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```


## the airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```


```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```
































