---
title: "Linear Regression"
author: "Clement Mugenzi"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(p8105.datasets)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```


# Some linear models


```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit the first linear model

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```





```{r}
fit

summary(fit)
coef(fit)
summary(fit)$coef
```

tidythe results instead

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
# another way to tidy is to use glance.
fit %>% 
  broom::glance()
```


## Tak a look at factor...

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```


refit the last model 

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()
```

## diagnostics (all about the residuals)

boro against residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() + ylim(-500, 500)
```


stars against residuals

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() + ylim(-500, 500)
```


add some predictions 

```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

# Nesting data

Here, every increase in stars and how it affects price per boro.

```{r}
fit_interaction = 
  lm(price ~ stars * boro, data = nyc_airbnb) %>% 
  broom::tidy()

fit_interaction
```




```{r}
fit_interaction_1 = 
  nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
fit_interaction_1
```


Let's try to map this instead

```{r}
nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(boro, results) %>% 
  unnest(results)
```


```{r}
manhattan_nest_lm_res = 
  nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(neighborhood, results) %>% 
  unnest(results)
```

Here we are plotting neighbrohoods in manhattan and what it would cost if we moved from a private room to a shared room. it will cost less.

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```











































